---
title: "p8105_hw6_SL5454"
author: "Sining Leng"
date: "2024-11-26"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rnoaa)
library(modelr)
```

## Problem 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Bootstrap
```{r}
set.seed(123)  
boot_results =
  weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    model = map(strap, \(df) lm(tmax ~ tmin, data = df)), 
    r_squared = map_dbl(model, ~ broom::glance(.x)$r.squared), 
    log_beta = map_dbl(model, ~ log(coef(.x)[1] * coef(.x)[2])) 
  )
```

Distributions
```{r}
# Plot the distribution of R-squared
ggplot(boot_results, aes(x = r_squared)) +
  geom_histogram(bins = 30, color = "black", fill = "blue", alpha = 0.7) +
  labs(title = "Bootstrap Distribution of R-squared", x = "R-squared", y = "Frequency")

# Plot the distribution of log(beta0 * beta1)
ggplot(boot_results, aes(x = log_beta)) +
  geom_histogram(bins = 30, color = "black", fill = "red", alpha = 0.7) +
  labs(title = "Bootstrap Distribution of log(beta0 * beta1)", x = "log(beta0 * beta1)", y = "Frequency")
```

The distribution of R-squared appears to be approximately normal. The values of R-squared range between 0.88 and 0.94, with the highest frequency occurring aroung 0.91.

The distribution of log beta is also approximately normal. The values of log beta range from approximately 1.95 to 2.10, and the distribution is centered around approximately 2.00.

95% confidence intervals
```{r}
ci_r = quantile(boot_results$r_squared, c(0.025, 0.975))
ci_log = quantile(boot_results$log_beta, c(0.025, 0.975))

print(ci_r)
print(ci_log)
```

## Problem 2

```{r}
us_homicide =
  read_csv("./data/homicide-data.csv", na = c("Unknown"))|>
  janitor::clean_names()|>
  mutate(
    victim_age = as.numeric(victim_age),
    city_state = str_c(city, state, sep = ", "),
    solved = ifelse(disposition == "Closed by arrest", 1, 0)
    )|>
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
         victim_race %in% c("White", "Black")) 
```

Logistic regression for Baltimore
```{r}
baltimore = 
  us_homicide |>
  filter(city_state == "Baltimore, MD")

baltimore_model = 
  glm(solved ~ victim_age + victim_sex + victim_race, data = baltimore) 

baltimore_model |>
  broom::tidy(conf.int = TRUE, exponentiate = TRUE) |>
  filter(term == "victim_sexMale") |>
  select(term, estimate, conf.low, conf.high)

```

Logistic regression for each city
```{r}
city_models =
  us_homicide |>
  group_by(city_state) |>
  nest() |>
  mutate(
    model = map(data, \(x) glm(solved ~ victim_age + victim_sex + victim_race, data = x)),
    results = map(model, broom::tidy, conf.int = TRUE, exponentiate = TRUE)
  ) |>
  unnest(results) |>
  filter(term == "victim_sexMale") |>
  select(city_state, estimate, conf.low, conf.high)

print(city_models)
```

Plot the estimated ORs and their CIs for each city
```{r}
city_models |>
  ggplot(aes(x = estimate, y = reorder(city_state, estimate), xmin = conf.low, xmax = conf.high)) +
  geom_point() +
  geom_errorbar() +
  labs(title = "Odds Ratios for Solving Homicides",
       y = "City", x = "Adjusted Odds Ratio")
```

Albuquerque, NM has the largest OR for solving homicides. New York, NY has the lowest OR for solving homicides. The first four cities have ORs greater than 1, which indicate that male victims are more likely to have their homicides solved than female victims. Most cities have ORs close to 1, with the confidence intervals either overlapping 1 or extending to the right or left. The overall trend suggests that females may have high homicide resolution in most city.

## Problem 3
```{r}
baby_bw =
  read_csv("./data/birthweight.csv", na = c("", "NA", "."))|>
  janitor::clean_names() |>
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    mrace = factor(mrace),
    malform = factor(malform),
    .drop = TRUE
  )
```

